State-space PTA

### 2023-04-17 docs/manuscript/paper.tex
MCMC expts

\subsection{Parameter estimation on synthetic data}\label{sec:param_estimation}
We are now in a position to try to infer the parameters of a GW system. We take our NANOGrav PTA and create a synthetic noisy dataset using the parameters described in Table \ref{tab:toy_example_parameters}.
\begin{table}
	\centering
	\begin{tabular}{lc}
		Parameter & Value  \\
		\hline
		$\omega$       & $5 \times 10^{-7}$  \\
		$\alpha$          & $1.0$  \\
		$\delta$              & $1.0$   \\
		$\psi$              & $2.50$  \\
		$\iota$             & $1.0$  \\
		$\Phi_0$          & $0.20$  \\
		$h$ & 1e-2 \\
		$\sigma_{\rm p}$ & $10^{-13}$ \\
		$\sigma_{\rm m}$ & $10^{-10}$ \\
		$T_{obs}$ & 10 \text{ years} \\
		$\Delta t$ & 7 \text{ days} \\
		\hline
	\end{tabular}
	\caption{GW parameters used for generating synthetic data. There is nothing special about these parameters - they are just chosen arbitrarily.}
	\label{tab:toy_example_parameters}
\end{table}
\noindent Given this synthetic data, we can try to use our KF + NS approach to recover some of the parameters. The results for inference on 5 parameters, $\omega. \Phi_0, \psi, \iota, h$ are shown in Fig \ref{fig:corner}. \textcolor{red}{TK: likelihood plots for each parameter could also be of interest to include here? Need to expand this section greatly for more astrophysical systems and more unknown parameters}
\begin{figure*}
	\includegraphics[width=0.8\textwidth]{images/corner_example}
	\caption{Example corner plot. Aside: for this run the $\sigma_p$ value fed to the filter is different from that used to generate the data.}
	\label{fig:corner}
\end{figure*}

@@

\begin{figure}
	%\centering % Not needed
	\begin{subfigure}[b]{1\columnwidth}
		\includegraphics[width=\textwidth]{images/snr_canonical}
		\caption{}
		\label{fig:6MB_BFS}
	\end{subfigure}
	\\
	\begin{subfigure}[b]{1\columnwidth}
		\includegraphics[width=\textwidth]{images/snr_canonical_1psr}
		\caption{}
		\label{fig:25MB_bfs}
	\end{subfigure}
	\caption{Likelihood ratio vs strain for \textit{(a)} full PTA and \textit{(b)} a single randomly chosen pulsar. Horizontal dashed line shows the minimum detectable cutoff, vertical dashed line is the corresponding GW strain.}
	\label{fig:snr_detection}
\end{figure}

>>>>

\subsection{Parameter estimation on synthetic data}\label{sec:param_estimation}
We are now in a position to try to infer the parameters of a GW system. We take our NANOGrav PTA and create a synthetic noisy dataset using the parameters described in Table \ref{tab:toy_example_parameters}.
\begin{table}
	\centering
	\begin{tabular}{lc}
		Parameter & Value  \\
		\hline
		$\omega$       & $5 \times 10^{-7}$  \\
		$\alpha$          & $1.0$  \\
		$\delta$              & $1.0$   \\
		$\psi$              & $2.50$  \\
		$\iota$             & $1.0$  \\
		$\Phi_0$          & $0.20$  \\
		$h$ & 1e-2 \\
		$\sigma_{\rm p}$ & $10^{-13}$ \\
		$\sigma_{\rm m}$ & $10^{-10}$ \\
		$T_{obs}$ & 10 \text{ years} \\
		$\Delta t$ & 7 \text{ days} \\
		\hline
	\end{tabular}
	\caption{GW parameters used for generating synthetic data. There is nothing special about these parameters - they are just chosen arbitrarily.}
	\label{tab:toy_example_parameters}
\end{table}
\noindent Given this synthetic data, we can try to use our KF + NS approach to recover some of the parameters. The results for inference on 5 parameters, $\omega. \Phi_0, \psi, \iota, h$ are shown in Fig \ref{fig:corner2}. \textcolor{red}{TK: likelihood plots for each parameter could also be of interest to include here? Need to expand this section greatly for more astrophysical systems and more unknown parameters}
%\begin{figure*}
%	\includegraphics[width=0.8\textwidth]{images/corner_example}
%	\caption{Example corner plot. Aside: for this run the $\sigma_p$ value fed to the filter is different from that used to generate the data.}
%	\label{fig:corner}
%\end{figure*}

\begin{figure*}
	\includegraphics[width=0.8\textwidth]{images/canonical_example}
	\caption{Example corner plot. Aside: for this run the $\sigma_p$ value fed to the filter is different from that used to generate the data.}
	\label{fig:corner2}
\end{figure*}

@@

\begin{figure}
	\includegraphics[width=\columnwidth]{images/snr_canonical}
	\caption{Likelihood ratio vs strain for \textit{(a)} full PTA and \textit{(b)} a single randomly chosen pulsar. Horizontal dashed line shows the minimum detectable cutoff, vertical dashed lines are the corresponding GW strains.}
	\label{fig:SNR}
\end{figure}

\begin{figure*}
	\includegraphics[width=0.8\textwidth]{images/snr_mollewide}
	\caption{stuff}
	\label{fig:mollewide}
\end{figure*}

%
%
%
%\begin{figure}
%	%\centering % Not needed
%	\begin{subfigure}[b]{1\columnwidth}
%		\includegraphics[width=\textwidth]{images/snr_canonical}
%		\caption{}
%		\label{fig:6MB_BFS}
%	\end{subfigure}
%	\\
%	\begin{subfigure}[b]{1\columnwidth}
%		\includegraphics[width=\textwidth]{images/snr_canonical_1psr}
%		\caption{}
%		\label{fig:25MB_bfs}
%	\end{subfigure}
%	\caption{}
%	\label{fig:snr_detection}
%\end{figure}
